\documentclass{sigcomm}

\usepackage{todonotes}
\usepackage{algorithm}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage{mdframed}
\usepackage{amsmath}
\usepackage{paralist}
\input{bnf}

\newtheorem{defn}{\textbf{Definition}}
\newtheorem{thm}{\textbf{Theorem}}
\newtheorem{cor}{\textbf{Corollary}}
\newtheorem{lemma}{\textbf{Lemma}}

% \newcommand{\AND}{{\sf AC$^{\mbox{{\small 3}}}$N}}
\newcommand{\sink}{{\sf CCNSink}}

\begin{document}

% ccn gateway and bridge
\title{CCNSink: An Application-Layer Gateway for TCP/IP and Content Centric Network Interoperability}

\numberofauthors{1} 
\author{
\alignauthor
Christopher A. Wood\\ %\titlenote{NSF GRFP blurb.}
       \affaddr{University of California Irvine}\\
       \affaddr{Irvine, CA, USA}\\
       \email{woodc1@uci.edu}
}

\date{\today}

\maketitle
\begin{abstract}
With the growing presence of data streaming services and applications in today's Internet, content-centric networks (CCNs) are an increasingly attractive design alternative to the traditional IP-based host-oriented architecture. CCNs emphasize content by making it directly addressable and routable within the network, in contrast to addressable hosts and interfaces. This fundamental difference leads to vastly different mechanisms to publish and retrieve content and enable peer-to-peer communication. Named Data Networking (NDN) and its sibling implementation - CCNx - is one particular CCN design that has received considerable academic and industry attention. Despite the many promising benefits, there has been little research into the NDN deployment strategy. Clearly, an incremental deployment strategy is the only viable solution. During this integration phase, however, there will undoubtedly be a need for IP-based (NDN-based) hosts to communicate with and retrieve content from NDN-based (IP-based) hosts. To this end, we present an IP/NDN gateway to support interoperability between these different networking architectures with minimal application and transport layer modifications via semantic translation between the communication mechanisms used in both networks. The performance overhead induced by this gateway is studied in unidirectional and bidirectional communication settings.
\end{abstract}

\category{H.4}{TODO}{TODO}
\category{D.2.8}{TODO}{TODO}[TODO]

\terms{NDN/CCN; CCN Deployment; Network Gateway}

%\keywords{TODO} % NOT required for Proceedings

\input{01-intro}
\input{02-prelims}
\input{03-design}
\input{04-implementation}
\input{05-performance}

\section{Conclusion}
TODO

% \section{Acknowledgments}

\bibliographystyle{abbrv}
\bibliography{ref}  % sigproc.bib is the name of the Bibliography in this case


\end{document}


